---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# WebCMap

WebCMap is a highly efficient platform designed for query extended CMap, renowned for its ultra-fast computation speed and minimal resource consumption. It aims to provide users with a convenient and reliable solution for connectivity mapping analysis. Its main features and objectives include:

1. Blazing-Fast Computation: Leveraging advanced algorithm optimization and an efficient web-accelerated CMap architecture, WebCMap achieves fast in connectivity mapping large-scale signature data, significantly enhancing research efficiency and saving users' time.

2. Low Resource Requirements: The platform is designed with a focus on optimizing computational resources, ensuring smooth operation even on standard hardware configurations, thereby lowering user barriers and hardware costs.

3. Accurate Connectivity Analysis: Users can input query signature and efficiently mapping them with extended CMap. Six kinds of connectivity methods and another meta score are computed to accurately identify candidate signatures that are positively or negatively correlated with the query signature.

4. Diverse Application Scenarios: The platform is suitable for various fields, including drug repurposing, disease mechanism research, and biomarker discovery, helping researchers quickly screen potential drug candidates and similar drug/toxic/compound searching.

## Installation

You can install the development version of WebCMap like so:

``` r
# devtools::install_github("geneprophet/WebCMap")
```

or download the source package
``` r
# install.packages("/path/to/WebCMap_0.1.0.tar.gz", repos = NULL, type = "source")
```


## Example

This is a basic example demonstrating how to screen candidate drugs for coronary artery disease (CAD) using WebCMap:


```{r example}
# load WebCMap
library(WebCMap)
# load the example query_signature, which is derived from TWAS analysis of CAD (PMID:28209224)
data(query_signature)

head(query_signature)

# run the negative connectivity analysis
res = run_negative_CMap(query_signature = query_signature,K=50,cores=10)

head(res)

```


Visualization of CAD-lisofylline pair:
```{r filter}
#filter the CAD-lisofylline pair:
data = res[res$cmap_name=="lisofylline",]
```
Radar plot
```{r Radar, echo = FALSE}
radar_plot(data)
```
GSEA plot
```{r GSEA, echo = FALSE}
gsea_plot(data=data,query_signature=query_signature, K = 50)
```
Venn plot
```{r Venn, echo = FALSE}
venn_plot(data=data,query_signature=query_signature, K = 50)
```

